Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-08 paper/main.tex
correct typos

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging
(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different perceptual and cognitive
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways that process
different kind of visual information:
% dorsal vs ventral pathway
a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
ventral stream (the ``what pathway'') that leads into the temporal lobe
\citep{goodale1992separate, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when participants view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural, aminoff2013role}).
% \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.

@@

% summary if literature review
Taken together, the literature suggest that the PPA does not exclusively respond to
visually presented spatial information.
% three things in common
However, the reviewed studies share three common aspects:
% designed stimulus set
first, they employed a small set of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used a block-design paradigm to maximize detection power.
Third, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an explicit
perceptual task, experience our rich, multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures is also present under more
natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both \textit{visual and
auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and naturalistic
auditory stimulation. The audio-description maintains the naturalistic nature of
the movie stimulus, but limitted to the auditory domain.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets with
BOLD fMRI data from naturalistic and conventional block-design stimulation of
the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a conventional visual localizer
for each individual, because all three operationalization capitalize on events
that should evoke the cognitive processing of spatial information.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

% DISABLE RESULTS
%% results: group
%On a group average level,
%% operationalization in naturalistic stimuli
%results demonstrate that our approach to operationalize spatial perception
%during two naturalistic stimuli lead to increased hemodynamic activity in the
%PPA.
%% anterior vs. posterior
%On both a group and individual participant level, the comparison of results from the
%three datasets also suggests functional differences between the anterior and
%posterior PPA.
%% what does it mean
%The current data add evidence to the hypothesis that the PPA might consist of
%submodules that work together during visual perception of landscapes (cf.
%\citep{baldassano2013differential}).
%%
%Lastly, our results suggest that the PPA's anterior part can be localized in
%individual participants by contrasting high-level semantic information occurring in
%an auditory naturalistic stimulus.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compared results from whole-brain GLM analyses of
the movie and the audio-description to a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Additional analyses of the robustness of the results presented here are
available as supplementary materials.

@@

%#11 question
The fact that clusters of responses to the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
immanent in both visual and verbal stimuli.

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
The current analyses were carried out on the same preprocessed fMRI data that were used
for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
 \citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly
available annotation of its speech content \citep{hausler2021studyforrest} by
classifying concrete and countable nouns that the narrator uses to describe the
movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and
examples can be seen in Table~\ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses these
words to indicate a switch from one setting to another (e.g. ``[a] physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{setting\_new} or \texttt{setting\_rec}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories
(see Table~\ref{tab:events}).  These event categories were then used to model
hemodynamic responses.

@@

% low-level confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the movie stimulus, we computed the mean luminance (arbitrary units,
average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
mean luminance of each frame's left and right half, the difference in mean
luminance of the lower and upper half.  As an indicator of visual change, we
compute perceptual fingerprints for each movie frame using the pHash library
\citep{zauner2010implementation} and recorded the cumulative bitwise
difference to the previous frame.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square volume averaged across the length of every movie frame
(\unit[40]{ms}).

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; see Table~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimates (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, analysis scripts to generate the results, and
results as Datalad \citep{datalad} datasets, published to or linked from the
GIN repository
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
Unthresholded $Z$-maps of all contrasts
can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

@@

% speech anno
\item Häusler, C. O. \& Hanke M. \emph{OSF}
\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
(2020).

@@

In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

Several contrasts yielded significant clusters in superior temporal cortices
(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
% AD: auditory cortices
Further, contrasts that compare, possibly among others, nouns indicating a
switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
non-spatial categories yielded significant clusters in superior temporal
cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
% interpretation 1
This suggests that variance correlating with lower level auditory processes was
not averaged out across events and the employed nuisance regressors did not
capture this variance appropriately.
% interpretation 2
Another possibility might be that increased hemodynamic activity in superior
temporal cortices reflect a bias towards lower-level auditory perceptual
processes on the positive side of the GLM contrasts.
% soundscape
Increased activity in primary and secondary auditory cortices could be
attributed to changes in the soundscape that possibly accompany the narrator
when he is indicating the switch to another setting by describing its identity
or layout.

@@

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for the specificity of the main finds within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(see Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster, suggesting that
the observed differential hemodynamic response in the PPA for events defined
by particular movie cuts is not observed for other arbitrarily selected time point
in the movie.

>>>>

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging
(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different perceptual and cognitive
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways that process
different kind of visual information:
% dorsal vs ventral pathway
a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
ventral stream (the ``what pathway'') that leads into the temporal lobe
\citep{goodale1992separate, mishkin1982contribution}.

\todo[inline]{Goodale and Milner (1992), which is literally a call for what and
    how pathways. The function of these pathways remains in dispute but its
    clear that where (spatial processing) must take place in both streams. You
should probably acknowledge that.}
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when participants view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural, aminoff2013role}).
% \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.

@@

% summary if literature review
Taken together, the literature suggest that the PPA does not exclusively respond
to visually presented spatial information.
% three things in common
However, the reviewed studies share three common aspects:
% designed stimulus set
1) they employed a small set of carefully chosen and conceptualized stimuli,
% block-design
2) used a block-design paradigm to maximize detection power, and
% task
3) they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an explicit
perceptual task, experience our rich, multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.

% open question
In this study, we investigate whether increased hemodynamic activity in the PPA
that is usually detected by contrasting blocks of pictures is also present under
more natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both
\textit{visual and auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The current operationalization of visual spatial perception is based on an
annotation of cuts and depicted locations in the audio-visual movie ``Forrest
Gump'' \citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{haeusler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and
naturalistic auditory stimulation. The audio-description maintains the
naturalistic nature of the movie stimulus, but limited to the auditory domain.
% current GLM contrasts
We applied model-based, mass-univariate analyses to BOLD fMRI data from both
naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}.
% comparison to previous GLM
We compare current results to results from a previously performed model-based,
mass-univariate analysis that was applied to data from a conventional
block-designed functional localizer paradigm that was performed with the same
set of participants \citep{sengupta2016extension}.
% intro to hypo a
Similarly to the functional localizer, we currently also capitalize on events
that should evoke the cognitive processing of spatial information.
% hypo a
Thus, we hypothesized that our whole-brain analyses would reveal increased
hemodynamic activity in medial temporal regions that were defined functionally
defined as the PPA by the previous analysis of the data from the block-designed
localizer \citep{sengupta2016extension}.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

% DISABLE RESULTS
%% results: group
%On a group average level,
%% operationalization in naturalistic stimuli
%results demonstrate that our approach to operationalize spatial perception
%during two naturalistic stimuli lead to increased hemodynamic activity in the
m%PPA.
%% anterior vs. posterior
%On both a group and individual participant level, the comparison of results from the
%three datasets also suggests functional differences between the anterior and
%posterior PPA.
%% what does it mean
%The current data add evidence to the hypothesis that the PPA might consist of
%submodules that work together during visual perception of landscapes (cf.
%\citep{baldassano2013differential}).
%%
%Lastly, our results suggest that the PPA's anterior part can be localized in
%individual participants by contrasting high-level semantic information occurring in
%an auditory naturalistic stimulus.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compared results from whole-brain GLM analyses of
the movie and the audio-description to a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Additional analyses of the robustness of the results presented here are
available as supplementary materials.

@@

%#11 question
The fact that clusters of responses to the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects inherent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
inherent in both visual and verbal stimuli.

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
The current analyses were carried out on the same preprocessed fMRI data that were used
for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
 \citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly
available annotation of its speech content \citep{haeusler2021studyforrest} by
classifying concrete and countable nouns that the narrator uses to describe the
movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and
examples can be seen in Table~\ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses these
words to indicate a switch from one setting to another (e.g. ``[a] physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{setting\_new} or \texttt{setting\_rec}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories
(see Table~\ref{tab:events}).  These event categories were then used to model
hemodynamic responses.

@@

% low-level confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the movie stimulus, we computed the mean luminance (arbitrary units,
average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
mean luminance of each frame's left and right half, the difference in mean
luminance of the lower and upper half. As an indicator of visual change, we
computed perceptual fingerprints for each movie frame using the pHash library
\citep{zauner2010implementation} and recorded the cumulative bitwise
difference to the previous frame.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square volume averaged across the length of every movie frame
(\unit[40]{ms}).

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; see Table~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant- and run-specific motion estimates (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, analysis scripts to generate the results, and
results as Datalad \citep{datalad} datasets, published to or linked from the
GIN repository
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
Unthresholded $Z$-maps of all contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

\todo[inline]{Following dataset are added to references.bib}
\todo[inline]{reference to cut anno might be retundant}
\todo[inline]{propably, cite them above in the manuscript where it makes sense}

Cited here, so they show in the references (see at end of references):
\citep{haeusler2016cutdata, haeusler2021speechdata, hanke2014ds000113, sengupta2016ds000113c, hanke2016ds000113d}

@@

% speech anno
\item Häusler, C. O. \& Hanke M. \emph{OSF}
\href{https://doi.org/10.17605/OSF.IO/GFRME}{GFRME}
(2020).

@@

In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

Several contrasts yielded significant clusters in superior temporal cortices
(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
% AD: auditory cortices
Further, contrasts that compare, possibly among others, nouns indicating a
switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
non-spatial categories yielded significant clusters in superior temporal
cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
% interpretation 1
This suggests that variance correlating with lower level auditory processes was
not averaged out across events (e.g. switches to another setting might often not
just cued by the narrator but also by a change of the soundscape or cued by a
the start of a new song) and the employed nuisance regressors did not capture
this variance appropriately.
% interpretation 2
Another possibility might be that increased hemodynamic activity in superior
temporal cortices reflect a bias towards lower-level auditory perceptual
processes on the positive side of the GLM contrasts.
% soundscape
Increased activity in primary and secondary auditory cortices could be
attributed to changes in the soundscape that possibly accompany the narrator
when he is indicating the switch to another setting by describing its identity
or layout.

@@

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for the specificity of the main findings within the movie fMRI data, we
created four contrasts that compared hemodynamic activity during frames within
movie shots (\texttt{no\_cut} category) with movie cut related categories (see
Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster, suggesting that the
observed differential hemodynamic response in the PPA for events defined by
particular movie cuts is not observed for other arbitrarily selected time point
in the movie.
